Response to decision letter

### 2023-06-03 submission/final-captions.tex
fix typos

Fringillidae median summary chronogram generated with DateLife. The original topology has 289 tips and 253 nodes, from which 194 have age data from at least one published chronogram. In total, 19 different chronograms from 13 different studies contribute 818 age data points, which were summarized to obtain a single value for each one of the 194 nodes with age data. From the 194 summary ages available, 21 were not used as calibrations (asterisk), because they were older than a parent node and/or younger than a descendant node; the remianing 173 were used as secondary calibrations (forward slash) with the Branch Length Adjuster (BLADJ ) software from Webb et al., (\protect\hyperlink{ref-Webb2008}{2008}).

>>>>

Fringillidae median summary chronogram generated with DateLife. The original topology has 289 tips and 253 nodes, from which 194 have age data from at least one published chronogram. In total, 19 different chronograms from 13 different studies contribute 818 age data points, which were summarized to obtain a single value for each one of the 194 nodes with age data. From the 194 summary ages available, 21 were not used as calibrations (asterisk, *), because they were older than a parent node or younger than a descendant node; the remaining 173 summary ages were used as secondary calibrations (forward slash, /) with the Branch Length Adjuster (BLADJ) software from Webb et al., (\protect\hyperlink{ref-Webb2008}{2008}).
